Behavior Driven Development in Haskell

### 2012-05-25 paper.tex
Add affiliation
Minor cleanup of "terminology" section.

\authorinfo{Simon HENGEL}
           {TBD: Affiliation}
           {TBD: Email}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\begin{description}
\item[developer] programmers who develop libraries
\item[users] programmers who use libraries
%%\item[unit test] tests for individual programs or libraries.
\item[example] Typical usage of functions. (TBD(@sol): more vocal)
\item[property] Invariants which functions have.
\item[behavior] How do functions behave for users. Behavior can be shown by using both examples and properties.
\item[documentation] Explanation of functions.
\end{description}

>>>>

\authorinfo{Simon HENGEL}
           {Freelance Software Developer}
           {sol@typeful.net}
%% \authorinfo{Trystan SPANGLER}
%%            {TBD: Affiliation}
%%            {TBD: Email}
\authorinfo{Kazuhiko YAMAMOTO}
           {IIJ Innovation Institute Inc.}
           {kazu@iij.ad.jp}

@@

\begin{description}
\item[developer]
    A programmer who develops a library.
\item[user]
    A programmer who uses a library.
%%\item[unit test] tests for individual programs or libraries.
\item[example]
    A typical usage example of a function.
\item[property]
    An invariant of a function.
\item[behavior]
    How does a function behave from a users point of view. Behavior can be
    shown by using both examples and properties.
\item[documentation] Explanation of functions.
\end{description}
